\LaTeX\ Author Guidelines for ICCV Proceedings

### 2021-03-16 chapters/1_intro.tex
Integrate last Fred's comments

\begin{figure*}[t]
\centering
\includegraphics[width=0.98\textwidth]{figs/intro_image_v6.pdf} % left bottom right top
\caption{\textbf{(a)} Some iterations of \algname{}, the proposed Generalized Agglomerative Algorithm for Signed Graph Partitioning, on a toy graph with attractive/positive (green) and repulsive/negative (red) interactions. At each iteration, the yellow edge with highest interaction is contracted. An example with sum linkage criterion is shown. \textbf{(b)} List of linkage criteria used in this paper (see definitions in Table~\ref{tab:linkage-criteria} below), demonstrated on two small clusters.  \textbf{(c)} Application of \algname{} to instance segmentation: we show raw data from the CREMI 2016 neuron-segmentation challenge and some predictions of our CNN model, where white pixels represent boundary evidence. \textbf{(d)} 
Seemingly similar linkage criteria can result in very different clustering dynamics, as shown in this example: color coded sequence of merges from early (white) via late (brown) to never (black).
% \algname{} agglomeration order for sum and average linkage: we show which pairs of neighboring pixels were merged first (white), later on (brown/red), or never (black).
\label{fig:intro_figure}}
\end{figure*}

@@

        \end{tabular}
    \end{subtable} 
    \caption{Conceptual contribution: Properties of clustering algorithms included in the proposed \algname{} framework, given a linkage criterion, a type of graph (signed or unsigned) and the optional use of cannot-link constraints. New constrained hierarchical clustering algorithms (HCC) proposed in this paper are highlighted in yellow. For algorithms typeset in bold font we prove that they define an ultrametric on the graph (Eq.~\ref{eq:UM_def}). For algorithms in the green box we show that they are weight-shift invariant (Prop.~\ref{prop:weight_shift_invariant}). 
    Notation: given a signed graph $\mathcal{G}(V,E, w_e)$, we denote as $E_{ij}=(S_i \times S_{j}) \cap E$ the set of edges connecting two clusters $S_i \subseteq V$, $S_j \subseteq V$. } 
    \label{tab:linkage-criteria}
\end{table*}

@@

Our first contribution is a simple theoretical framework that generalizes over agglomerative algorithms for signed graphs by linking them to hierarchical clustering (HC) on unsigned graphs (Section \ref{sec:algorithm}). This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and \emph{cannot-link constraints} (see Fig.~\hyperref[fig:intro_figure]{\ref*{fig:intro_figure}a}, \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}b}, and Table~\ref{tab:linkage-criteria}). 
As second contribution, in Section \ref{sec:alg_update_rules}, we formally prove that some of the combinations correspond to existing clustering algorithms, and introduce new algorithms for combinations which have not been explored before. By analyzing their theoretical properties, we also show which ones define an ultrametric on the graph (see Table~\ref{tab:linkage-criteria}).

>>>>

\begin{figure*}[t]
\centering
\includegraphics[width=0.92\textwidth]{figs/intro_image_v6.pdf} % left bottom right top
\caption{\textbf{(a)} Some iterations of \algname{} on a graph with attractive (green) and repulsive (red) interactions. At each iteration, the yellow edge with highest interaction is contracted (example with sum linkage criterion is shown). \textbf{(b)} Linkage criteria used in this paper demonstrated on two small clusters (see definitions in Table~\ref{tab:linkage-criteria} below).  \textbf{(c)} Application of \algname{} to instance segmentation: we show raw data from the CREMI neuron-segmentation challenge and some predictions of our CNN model, where white pixels represent boundary evidence. \textbf{(d)} 
Seemingly similar linkage criteria can result in very different clustering dynamics, as shown in this example: color coded sequence of merges from early (white) via late (brown) to never (black).
% \algname{} agglomeration order for sum and average linkage: we show which pairs of neighboring pixels were merged first (white), later on (brown/red), or never (black).
\label{fig:intro_figure}}
\end{figure*}

@@

        \end{tabular}
    \end{subtable} 
    \caption{Conceptual contribution: Properties of clustering algorithms included in the proposed \algname{} framework, given a linkage criterion, a type of graph (signed or unsigned) and the optional use of cannot-link constraints. New constrained hierarchical clustering algorithms (HCC) proposed in this paper are highlighted in yellow. For algorithms typeset in bold font we prove that they define an ultrametric on the graph (Eq.~\ref{eq:UM_def}). For algorithms in the green box we show that they are weight-shift invariant (Prop.~\ref{prop:weight_shift_invariant}). 
    Notation: 
    % given a signed graph $\mathcal{G}(V,E, w_e)$, we denote as 
    $E_{ij}=(S_i \times S_{j}) \cap E$ denotes the set of edges connecting two clusters $S_i, S_j \subseteq V$. } 
    \label{tab:linkage-criteria}
\end{table*}

@@

Our first contribution is a simple theoretical framework that generalizes over agglomerative algorithms for signed graphs by linking them to hierarchical clustering (HC) on unsigned graphs (Section \ref{sec:algorithm}). This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and \emph{cannot-link constraints} (see Fig.~\hyperref[fig:intro_figure]{\ref*{fig:intro_figure}a}, \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}b}, and Table~\ref{tab:linkage-criteria}). 
As second contribution, in Section \ref{sec:alg_update_rules}, we formally prove that some of the combinations correspond to existing clustering algorithms, and introduce new algorithms for combinations which have not been explored before. By analyzing their theoretical properties, we also show that some of them define an ultrametric on the graph (see Table~\ref{tab:linkage-criteria}).

### 2021-03-16 chapters/3_algorithm.tex
Integrate last Fred's comments

\paragraph{Average, Single, and Complete Linkage} -- These three linkage criteria have been throughly studied on unsigned graphs, but never on signed graphs. In the recent related work \cite{chehreghani2020hierarchical}, the authors prove that applying these three linkage methods to a signed graph is equivalent to applying them to the unsigned graph obtained by shifting all edge weights by a constant.  Here, we prove which of the algorithms included in our generalized framework have this invariance-property:
\begin{restatable}{prop}{invariantAlgs}
\label{prop:weight_shift_invariant}
We call an agglomerative algorithm ``weight-shift invariant'' if the structure of the merging tree $T$ returned by the algorithm is invariant w.r.t. a shift of all edge weights $w_e$  by a constant $\alpha\in \mathbb{R}$. Among the versions of \algname{} studied in this paper, only hierarchical clustering using Average (HC-Avg), Single (HC-Single), and Complete linkage (HC-Complete) are weight-shift-invariant (see algorithms included in the green box in Table~\ref{tab:linkage-criteria}).
\end{restatable}
\noindent To our knowledge, Average and Single linkage methods have never been combined with cannot-link constraints on signed graphs, so we name these algorithms \emph{HCC-Avg} and \emph{HCC-Single}. In Lemma \ref{lemma:absMax_and_complete_property} (Appendix \ref{sec:proposition_proofs}), we prove that with Complete linkage the agglomeration order does not change whether constraints are introduced or not.

>>>>

\paragraph{Average, Single, and Complete Linkage} -- These three linkage criteria have been throughly studied on unsigned graphs, but never on signed graphs. In recent independent related work \cite{chehreghani2020hierarchical}, the authors prove that applying these three linkage methods to a signed graph is equivalent to applying them to the unsigned graph obtained by shifting all edge weights by a constant.  Here, we prove which of the algorithms studied here is ``intrinsically'' signed and do not have this invariance-property:
\begin{restatable}{prop}{invariantAlgs}
\label{prop:weight_shift_invariant}
We call an agglomerative algorithm ``weight-shift invariant'' if the structure of the merging tree $T$ returned by the algorithm is invariant w.r.t. a shift of all edge weights $w_e$  by a constant $\alpha\in \mathbb{R}$. Among the versions of \algname{} studied in this paper, only hierarchical clustering using Average (HC-Avg), Single (HC-Single), and Complete linkage (HC-Complete) are weight-shift-invariant (see algorithms included in the green box in Table~\ref{tab:linkage-criteria}).
\end{restatable}
\noindent To our knowledge, Average and Single linkage methods have never been combined with cannot-link constraints on signed graphs, so we name these algorithms \emph{HCC-Avg} and \emph{HCC-Single}. On the other hand, we prove that enforcing constraints with a Complete linkage does not change the final clustering (Lemma \ref{lemma:absMax_and_complete_property}, in Appendix).
% , we prove that with Complete linkage the agglomeration order does not change whether constraints are introduced or not.

### 2021-03-16 chapters/5_experiments_intro.tex
Integrate last Fred's comments

        \begin{tabular}{l  c  r  c  c  | r r r r r r}
        % \toprule
        &&&& %\multicolumn{1}{c}{}
        &\multicolumn{5}{c}{Multicut objective values of final clusterings (average across instances, lower is better)} \\
        Clustering problem & \makecell{Graph Type} & $\#I$ & $|V|$ & $|E|$  & \multicolumn{1}{r}{GAEC \cite{keuper2015efficient}} & HCC-Sum & MWS \cite{wolf2018mutex} & HC-Avg & HCC-Avg \\ \midrule
        \emph{Modularity Clustering} \cite{brandes2007modularity} & \emph{complete} & 6& 34-115 & 561-6555 & % \HollowBox & 
        -0.457 & -0.453 & -0.073 & \textbf{-0.467} & \textbf{-0.467} \\ 
        \emph{Image Segmentation} \cite{andres2011probabilistic} & \emph{rag} & 100 & 156-3764 &  439-10970  & % \HollowBox 
        \textbf{-2,955} & -2,953 & -2,901 & -2,903 & -2,896\\
        \emph{Knott-3D (150-300-450)} \cite{andres2012globally} & \emph{3D-rag} & 24 & 572-17k & 3381-107k & % \HollowBox & 
        \textbf{-36,667} & -36,652 & -35,200 & -35,957 & -35,631\\
        % \emph{Knott-3D-300} & \emph{3D-rag} & 8& & & \HollowBox\\
        % \emph{Knott-3D-450}& \emph{3D-rag} & 8 & & & \HollowBox\\  
        \emph{CREMI-3D-rag (OurCNN)}  & \emph{3D-rag} & 3& 134k-157k & 928k-1065k % & \CrossedBox 
        & \textbf{-1,112,287} & \textbf{-1,112,286}& -1,109,731 & -1,112,177 & -1,112,100\\ 
        \emph{Fruit-Fly Level 1-4} \cite{pape2017solving} & \emph{3D-rag} & 4& 5m-11m & 28m-72m %& \HollowBox 
        & \textbf{-151,022} & -151,017 & -150,879 & -150,909 & -150,876\\
        \emph{CREMI-gridGraph (OurCNN)} & \emph{gridGraph} & 15& 39m & 140m %& \CrossedBox 
        & -73,317,601 & -73,328,867 & -73,330,568 & \textbf{-73,502,947} & -73,474,856\\
        \emph{Fruit-Fly Level Global} \cite{pape2017solving} & \emph{3D-rag} & 1& 90m & 650m % & \HollowBox 
        & \textbf{-151,688} & -151,596 & -146,315 & -150,466 & -150,171 \\
        % \emph{(CREMI-pixGrid-LSIMasksUNet)} & \emph{gridGraph} & 1 & & 4 & \CrossedBox\\
        % \emph{(CityScapesValidation-pixGrid)} & \emph{gridGraph} &  &  & & \CrossedBox\\
        % \emph{CREMI-test....}\\\midrule
        % \emph{Stochastic Block Model (synthetic)} & \emph{non-planar} &-&- & - & \CrossedBox \\
        % \emph{(epinions and slashdot?)} & \emph{dense?} &  & & & \HollowBox\\

@@

\textbf{Existing signed graphs}  -- We use clustering instances from the OpenGM benchmark \cite{kappes2013comparative} as well as biomedical segmentation instances \cite{pape2017solving}. The dataset \emph{Image Segmentation} contains planar region-adjacency-graphs (\emph{rag}) that are constructed from superpixel adjacencies of photographs. The \emph{Knott-3D} datasets contains \emph{3D-rags} arising from volume images acquired by electron microscopy (EM). The set \emph{Modularity Clustering} contains complete graphs constructed from clustering problems on small social networks. The \emph{Fruit-Fly} 3D-rag instances were generated from volume image scans of fruit fly brain matter. Instances \emph{Level 1-4} are progressively simplified versions of the global problem obtained via block-wise domain decomposition \cite{pape2017solving}.

@@

\textbf{3D-rag from CNN-predictions} -- Lastly, we use the predictions of our CNN model to generate three graph instances (one for each CREMI training sample, named \emph{CREMI-3D-rag} in Table~\ref{tab:datasets_and_energies}), which have very similar structure to the \emph{Knott-3D} and \emph{Fruit-Fly} instances.  We obtain these problems by using a pipeline that is very common in neuron segmentation: a watershed algorithm generates superpixels and from those a 3D region-adjacency graph is built, where edge weights are given by the CNN predictions averaged over the boundaries of adjacent superpixels (details in Appendix \ref{sec:cremi_details}). 
% them by first computing 2D supervoxels from the CNN predictions (using a watershed algorithm seeded at the maxima of the smoothed boundary distance transform) and then building a 3D region-adjacency graph, whose edge weights are given by the CNN affinities averaged over the boundaries of adjacent supervoxels.

@@

        \begin{subtable}[t]{0.29\textwidth}

@@

        \begin{tabular}[t]{lcccc}

@@

          & \makecell{ARAND\\error} & \makecell{VOI\\split} & \makecell{VOI\\merge}&  \makecell{Runtime\\(s)} \\ \midrule 

@@

        \vspace*{1em}

@@

\begin{subtable}[t]{.29\textwidth}

@@

        \vspace*{1em}
    \caption{\emph{CREMI-3D-rag (OurCNN)}}

@@

    \begin{subtable}[t]{.38\textwidth}

@@

        \begin{tabular}[t]{lcccc}

@@

          & \makecell{CREMI\\Score} & \makecell{ARAND\\error} & \makecell{VOI\\split} & \makecell{VOI\\merge}    \\ \midrule 
OurCNN: 3D-rag + LiftedMulticut & \textbf{0.221} & \textbf{0.108} & \textbf{0.339} & 0.115 \\
\emph{OurCNN: gridGraph + HCC-Avg} & 0.224 & 0.113 & 0.361 & 0.085  \\
\emph{OurCNN: gridGraph + HC-Avg}  & 0.224 & 0.114 &  0.364 & 0.083 \\
PNI CNN \cite{lee2017superhuman} & 0.228 & 0.116 & 0.345 & 0.106 \\
LSI-Masks \cite{bailoni2020proposal}  & 0.246 & 0.125 & 0.383 & 0.107  \\
\emph{OurCNN: 3D-rag + HCC-Avg} & 0.257 & 0.132 & 0.438& \textbf{0.063} \\  
\emph{OurCNN: 3D-rag + HC-Avg} & 0.262 & 0.135 & 0.448 & \textbf{0.063}   \\  

@@

MALA CNN + MC \cite{funke2018large} & 0.276  & 0.132 &0.490  & 0.089  \\
CRU-Net \cite{zeng2017deepem3d} & 0.566 & 0.229 & 1.081 &  0.389    \\

@@

    \caption{\textbf{Tables (a-b)}: Scores and run times of algorithms in the \algname{} framework on the \emph{CREMI-gridGraph} and \emph{CREMI-3D-rag} clustering problems: average linkage methods achieved the best accuracy. Measures shown are: Adapted-Rand error (ARAND, lower is better); Variation of Information (VOI) \cite{arganda2015crowdsourcing} (VOI-merge for under-clustering error and VOI-split for over-clustering error, lower values are better). \textbf{Table (c)}: Current leading entries in the CREMI challenge leaderboard (March 2021). CREMI-score is given by the geometric mean of (VOI-split + VOI-merge)  and ARAND error (lower is better).}

@@

@@

\textbf{Scores on CREMI instance-segmentation} -- 
SSBM graphs are \emph{non-planar}, and every edge has the same probability to be present in the graph. On the other hand, the \emph{gridGraph} and \emph{3D-rag} graphs of Table~\ref{tab:datasets_and_energies} are sparse and have a very regular structure: regardless of whether a node represents a pixel or a superpixel, it will only have edge connections with its neighbors in the image (up to a certain hop distance). 
Tables~\ref{tab:scores_gridGraph}-\ref{tab:scores_3drag} show that average linkage methods (HC-Avg, HCC-Avg) strongly outperform other methods on \emph{CREMI-gridGraph} instances and also achieve the best scores on \emph{CREMI-3D-rag} graphs. Sum-based linkage methods (GAEC, HCC-Sum) do not perform well on grid-graphs and often return under-clustered segments (see failure cases in Fig.~\ref{fig:failure_cases}). This suggests that the \emph{flooding strategy} observed previously in the sum-linkage methods performs poorly on grid-graphs, because in this setup edge weights are predicted by a CNN and noise is strongly spatially-correlated \footnote{This effect is not as strong on \emph{3D-rag} graphs, because edge weights are computed by averaging CNN predictions (and noise) over the boundaries of adjacent supervoxels.}.
To fully test this hypothesis, we conduct a set of experiments where the CNN predictions are perturbed by adding structured noise and simulating additional artifacts like ``holes'' in the boundary evidence\footnote{See Appendix \ref{sec:appendix_noise_gen} for details about how we perturbed the \emph{CREMI-gridGraph} problems by using Perlin noise \cite{perlin2001noise,perlin1985image}, which is one of the most common gradient noises used in procedural pattern generation.}. 
The plot in Fig.~\ref{fig:scores_structured_noise} confirms that HC-Avg and HCC-Avg perform well even in the presence of strong structured noise, followed by Sum-linkage algorithms and the Mutex Watershed algorithm (MWS). It is not a surprise that the AbsMax linkage used by MWS is not robust to this type of structured noise. However, the scores and runtimes in Table~\ref{tab:scores_gridGraph} prove how MWS can achieve competitive performances with considerably lower runtimes.

\begin{figure}
\centering
% \includegraphics[width=0.48\textwidth,trim=300 100 300 100, clip]{./figs/dendrograms/new_agglo_order_OLD.png} % left bottom right top
\includegraphics[width=0.48\textwidth,trim=80 10 60 0, clip]{./figs/dendrograms/new_agglo_order.png} % left bottom right top
\caption{Clustering dynamics and accuracy of GASP variations on stochastic block models. The dendrograms result from three versions of \algname{} (GAEC, MWS, and HC-Avg) on a synthetic graph generated with SSBM ($N=250$ nodes, edge probability $p=0.05$, flipping probability $\eta=0.1$).  Red and blue colors show which of the two equal-sized ground-truth communities each node belongs to. At the top, dendrograms are truncated at the level of the final clustering $\Pi^*$ returned by \algname{}. \label{fig:dendrograms}}
\end{figure}

\textbf{Results on CREMI challenge} -- 
Table~\ref{tab:cremi_leaderboard} shows that the HCC-Avg and HC-Avg clustering algorithms achieve state-of-the-art performances on the CREMI challenge, when combined with predictions of our CNN.
Most of the other entries (apart from \emph{LSI-Masks} \cite{bailoni2020proposal}) employ super-pixels based post-processing pipelines and cluster 3D-region-adjacency graphs. As we show in Table ~\ref{tab:scores_3drag}, using super-pixels considerably reduces the size of the clustering problem and, consequently, the post-processing time. 
However, our method operating directly on pixels (\emph{gridGraph+HCC-Avg}) achieves better performances than superpixel-based methods (\emph{3D-rag+HCC-Avg}) and does not require the parameter tuning necessary to obtain good super-pixels, which is usually highly dataset dependent.
To scale up our method operating on pixels, we divided each test-volume into four sub-blocks, and then combined the resulting clusterings by running the algorithms again on the combined graph.
The method \emph{3D-rag+LiftedMulticut} based on the lifted multicut approximation of \cite{beier2017multicut} achieves the best scores overall, but it takes into account different information through the lifted edge weights that also depend on additional raw-data and shape information from highly engineered super-pixels. 
% Note that the test volumes of the challenge contain several imaging artifacts that make segmentation particularly challenging.
% However: handcrafted and dataset dependent, performs better, no

@@

\begin{figure}
\centering
\includegraphics[width=0.48\textwidth,trim=90 10 60 0, clip]{./figs/comparison_GAEC_MWS_Avg.png} % left bottom right top
\caption{Failure cases of three versions of \algname{} (GAEC, MWS, and HC-Avg) applied to neuron segmentation. Only \emph{wrongly} segmented regions are highlighted in different warm colors. Red arrows point to wrongly split regions; yellow arrows point to false merge errors. HC-Avg returned the best segmentation. Data is 3D, hence the same color could be assigned to parts of segments that appear disconnected in 2D.  
\label{fig:failure_cases}}
\end{figure}

>>>>

        \begin{tabular}{l  c  r  c  c  | r r r r r r}
        % \toprule
        &&&& %\multicolumn{1}{c}{}
        &\multicolumn{5}{c}{Multicut objective values (average across instances, lower is better)} \\
        Clustering problem & \makecell{Graph Type} & $\#I$ & $|V|$ & $|E|$  & \multicolumn{1}{r}{GAEC \cite{keuper2015efficient}} & HCC-Sum & MWS \cite{wolf2018mutex} & HC-Avg & HCC-Avg \\ \midrule
        \emph{Modularity Clustering} \cite{brandes2007modularity} & \emph{complete} & 6& 34-115 & 561-6555 & % \HollowBox & 
        -0.457 & -0.453 & -0.073 & \textbf{-0.467} & \textbf{-0.467} \\ 
        \emph{Image Segmentation} \cite{andres2011probabilistic} & \emph{RAG} & 100 & 156-3764 &  439-10970  & % \HollowBox 
        \textbf{-2,955} & -2,953 & -2,901 & -2,903 & -2,896\\
        \emph{Knott-3D (150-300-450)} \cite{andres2012globally} & \emph{3D-RAG} & 24 & 572-17k & 3381-107k & % \HollowBox & 
        \textbf{-36,667} & -36,652 & -35,200 & -35,957 & -35,631\\
        % \emph{Knott-3D-300} & \emph{3D-RAG} & 8& & & \HollowBox\\
        % \emph{Knott-3D-450}& \emph{3D-RAG} & 8 & & & \HollowBox\\  
        \emph{CREMI-3D-RAG (OurCNN)}  & \emph{3D-RAG} & 3& 134k-157k & 928k-1065k % & \CrossedBox 
        & \textbf{-1,112,287} & \textbf{-1,112,286}& -1,109,731 & -1,112,177 & -1,112,100\\ 
        \emph{Fruit-Fly Level 1-4} \cite{pape2017solving} & \emph{3D-RAG} & 4& 5m-11m & 28m-72m %& \HollowBox 
        & \textbf{-151,022} & -151,017 & -150,879 & -150,909 & -150,876\\
        \emph{CREMI-gridGraph (OurCNN)} & \emph{gridGraph} & 15& 39m & 140m %& \CrossedBox 
        & -73,317,601 & -73,328,867 & -73,330,568 & \textbf{-73,502,947} & -73,474,856\\
        \emph{Fruit-Fly Level Global} \cite{pape2017solving} & \emph{3D-RAG} & 1& 90m & 650m % & \HollowBox 
        & \textbf{-151,688} & -151,596 & -146,315 & -150,466 & -150,171 \\
        % \emph{(CREMI-pixGrid-LSIMasksUNet)} & \emph{gridGraph} & 1 & & 4 & \CrossedBox\\
        % \emph{(CityScapesValidation-pixGrid)} & \emph{gridGraph} &  &  & & \CrossedBox\\
        % \emph{CREMI-test....}\\\midrule
        % \emph{Stochastic Block Model (synthetic)} & \emph{non-planar} &-&- & - & \CrossedBox \\
        % \emph{(epinions and slashdot?)} & \emph{dense?} &  & & & \HollowBox\\

@@

\textbf{Existing signed graphs}  -- We use clustering instances from the OpenGM benchmark \cite{kappes2013comparative} as well as biomedical segmentation instances \cite{pape2017solving}. The dataset \emph{Image Segmentation} contains planar region-adjacency-graphs (RAG) that are constructed from superpixel adjacencies of photographs. The \emph{Knott-3D} datasets contains 3D-RAGs arising from volume images acquired by electron microscopy (EM). The set \emph{Modularity Clustering} contains complete graphs constructed from clustering problems on small social networks. The \emph{Fruit-Fly} 3D-RAG instances were generated from volume image scans of fruit fly brain matter. Instances \emph{Level 1-4} are progressively simplified versions of the global problem obtained via block-wise domain decomposition \cite{pape2017solving}.

@@

\textbf{3D-RAG from CNN-predictions} -- Lastly, we use the predictions of our CNN model to generate three graph instances (one for each CREMI training sample, named \emph{CREMI-3D-RAG} in Table~\ref{tab:datasets_and_energies}), which have very similar structure to the \emph{Knott-3D} and \emph{Fruit-Fly} instances.  We obtain these problems by using a pipeline that is very common in neuron segmentation: a watershed algorithm generates superpixels and from those a 3D region-adjacency graph is built, where edge weights are given by the CNN predictions averaged over the boundaries of adjacent superpixels (details in Appendix \ref{sec:cremi_details}). 
% them by first computing 2D supervoxels from the CNN predictions (using a watershed algorithm seeded at the maxima of the smoothed boundary distance transform) and then building a 3D region-adjacency graph, whose edge weights are given by the CNN affinities averaged over the boundaries of adjacent supervoxels.

@@

        \begin{subtable}[t]{0.27\textwidth}

@@

        \begin{tabular}[t]{@{\hspace{0.7\tabcolsep}}l c @{\hspace{1\tabcolsep}} c @{\hspace{1.1\tabcolsep}} c @{\hspace{1\tabcolsep}} c @{\hspace{1\tabcolsep}}}

@@

          & ARAND & VOI & VOI&  Runtime \\ 
          & Error & split & merge&  (s) \\ \midrule 

@@

        \vspace*{1.1em}

@@

\begin{subtable}[t]{.27\textwidth}

@@

        \vspace*{1.1em}
    \caption{\emph{CREMI-3D-RAG (OurCNN)}}

@@

    \end{subtable} \hfill
    \begin{subtable}[t]{.43\textwidth}

@@

        \begin{tabular}[t]{l @{\hspace{1.2\tabcolsep}} c @{\hspace{1\tabcolsep}} c @{\hspace{1\tabcolsep}} c @{\hspace{0.8\tabcolsep}} c @{\hspace{1\tabcolsep}} c}
        % \begin{tabular}[t]{lcccc}

@@

        & Needs & CREMI& ARAND & VOI & VOI\\ 
          & superpixels? & Score & Error & split & merge\\ \midrule 
          % & \makecell{CREMI\\Score} & \makecell{ARAND\\error} & \makecell{VOI\\split} & \makecell{VOI\\merge}    \\ \midrule 
OurCNN: 3D-RAG + LiftedMulticut & \CrossedBox & \textbf{0.221} & \textbf{0.108} & \textbf{0.339} & 0.115 \\
\emph{GASP: OurCNN + gridGraph + HCC-Avg} & \HollowBox & 0.224 & 0.113 & 0.361 & 0.085  \\
\emph{GASP: OurCNN + gridGraph + HC-Avg}  & \HollowBox &0.224 & 0.114 &  0.364 & 0.083 \\
PNI CNN \cite{lee2017superhuman} & \CrossedBox &0.228 & 0.116 & 0.345 & 0.106 \\
LSI-Masks \cite{bailoni2020proposal}  & \HollowBox &0.246 & 0.125 & 0.383 & 0.107  \\
\emph{GASP: OurCNN + 3D-RAG + HCC-Avg} & \HollowBox &0.257 & 0.132 & 0.438& \textbf{0.063} \\  
\emph{GASP: OurCNN + 3D-RAG + HC-Avg} & \HollowBox &0.262 & 0.135 & 0.448 & \textbf{0.063}   \\  

@@

MALA CNN + MC \cite{funke2018large} & \CrossedBox & 0.276  & 0.132 &0.490  & 0.089  \\
CRU-Net \cite{zeng2017deepem3d} & \CrossedBox &0.566 & 0.229 & 1.081 &  0.389    \\

@@

    \caption{\textbf{Tables (a-b)}: Scores and run times of algorithms in the \algname{} framework on the \emph{CREMI-gridGraph} and \emph{CREMI-3D-RAG} clustering problems: average linkage methods achieved the best accuracy. Measures shown are: Adapted-Rand error (ARAND, lower is better); Variation of Information (VOI) \cite{arganda2015crowdsourcing} (VOI-merge for under-clustering error and VOI-split for over-clustering error, lower values are better). \textbf{Table (c)}: Current leading entries in the CREMI challenge leaderboard (March 2021). CREMI-score is given by the geometric mean of (VOI-split + VOI-merge)  and ARAND error (lower is better).}

@@

\textbf{Scores on CREMI instance-segmentation} -- 
SSBM graphs are \emph{non-planar}, and every edge has the same probability to be present in the graph. On the other hand, the \emph{gridGraph} and \emph{3D-RAG} graphs of Table~\ref{tab:datasets_and_energies} are sparse and have a very regular structure: regardless of whether a node represents a pixel or a superpixel, it will only have edge connections with its neighbors in the image (up to a certain hop distance). 
Tables~\ref{tab:scores_gridGraph}-\ref{tab:scores_3drag} show that average linkage methods (HC-Avg, HCC-Avg) strongly outperform other methods on \emph{CREMI-gridGraph} instances and also achieve the best scores on \emph{CREMI-3D-rag} graphs. Sum-based linkage methods (GAEC, HCC-Sum) have a two times higher ARAND error on grid-graphs and often return under-clustered segments (see failure cases in Fig.~\ref{fig:failure_cases}). This suggests that the \emph{flooding strategy} observed previously in the sum-linkage methods does not work on grid-graphs, because in this setup edge weights are predicted by a CNN and noise is strongly spatially-correlated \footnote{This effect is not as strong on \emph{3D-RAG} graphs, because edge weights are computed by averaging CNN predictions (and noise) over the boundaries of adjacent supervoxels.}.
To fully test this hypothesis, we conduct a set of experiments where the CNN predictions are perturbed by adding structured noise and simulating additional artifacts like ``holes'' in the boundary evidence\footnote{See Appendix \ref{sec:appendix_noise_gen} for details about how we perturbed the \emph{CREMI-gridGraph} problems by using Perlin noise \cite{perlin2001noise,perlin1985image}, which is one of the most common gradient noises used in procedural pattern generation.}. 
The plot in Fig.~\ref{fig:scores_structured_noise} confirms that HC-Avg and HCC-Avg perform well even in the presence of strong structured noise, followed by Sum-linkage algorithms and the Mutex Watershed algorithm (MWS). It is not a surprise that the AbsMax linkage used by MWS is not robust to this type of structured noise. However, the scores and runtimes in Table~\ref{tab:scores_gridGraph} prove how MWS can achieve high accuracy with considerably lower runtimes.

@@

\begin{figure}
\centering
% \includegraphics[width=0.48\textwidth,trim=300 100 300 100, clip]{./figs/dendrograms/new_agglo_order_OLD.png} % left bottom right top
\includegraphics[width=0.48\textwidth,trim=80 10 60 0, clip]{./figs/dendrograms/new_agglo_order.png} % left bottom right top
\caption{Clustering dynamics and accuracy of GASP variations on stochastic block models. The dendrograms result from three versions of \algname{} on a synthetic graph generated with SSBM ($250$ nodes, edge probability $p=0.05$, flipping probability $\eta=0.1$).  Red and blue colors show which of the two equal-sized ground-truth communities each node belongs to. At the top, dendrograms are truncated at the level of the final clustering $\Pi^*$ returned by \algname{}. \label{fig:dendrograms}}
\end{figure}

\textbf{Results on CREMI challenge} -- 
Table~\ref{tab:cremi_leaderboard} shows that the HCC-Avg and HC-Avg clustering algorithms achieve state-of-the-art accuracy on the CREMI challenge, when combined with predictions of our CNN.
Most of the other entries (apart from \emph{LSI-Masks} \cite{bailoni2020proposal}) employ super-pixels based post-processing pipelines and cluster 3D-region-adjacency graphs. As we show in Table ~\ref{tab:scores_3drag}, using super-pixels considerably reduces the size of the clustering problem and, consequently, the post-processing time. 
However, our method operating directly on pixels (\emph{gridGraph + HCC-Avg}) achieves better performances than superpixel-based methods (\emph{3D-RAG + HCC-Avg}) and does not require the parameter tuning necessary to obtain good super-pixels, which is usually highly dataset dependent.
To scale up our method operating on pixels, we divided each test-volume into four sub-blocks, and then combined the resulting clusterings by running the algorithms again on the combined graph.
The method \emph{3D-RAG + LiftedMulticut} based on the lifted multicut approximation of \cite{beier2017multicut} achieves the best scores overall, but it takes into account different information through the lifted edge weights that also depend on additional raw-data and shape information from highly engineered super-pixels. 
% Note that the test volumes of the challenge contain several imaging artifacts that make segmentation particularly challenging.
% However: handcrafted and dataset dependent, performs better, no

@@

\begin{figure}
\centering
\includegraphics[width=0.48\textwidth,trim=90 10 60 0, clip]{./figs/comparison_GAEC_MWS_Avg.png} % left bottom right top
\caption{Failure cases of three versions of \algname{} applied to neuron segmentation. Only \emph{wrongly} segmented regions are highlighted in different warm colors. Red arrows point to wrongly split regions; yellow arrows point to false merge errors. HC-Avg returned the best segmentation. Data is 3D, hence the same color could be assigned to parts of segments that appear disconnected in 2D.  
\label{fig:failure_cases}}
\end{figure}
